Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-01-16 4.exact_support_recovery/exact_support_recovery.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.
small typo

We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.  
Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in 
Section \ref{subsec:sufficient}.  A very general class of dependence structures characterized by the uniform relative stability concept will 
be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.

@@

%\section{Exact support recovery under AGG errors}
%\label{sec:boundary}
\input{4.exact_support_recovery/4.phase_transition_results.tex}
\input{4.exact_support_recovery/4.pointwise.minimax.tex}

@@

\section{Additional proofs}
\label{suppsec:proofs}
\input{4.exact_support_recovery/4.proofs-examples.tex}
\input{4.exact_support_recovery/4.proofs-convexity.tex}

>>>>

We focus on exact support recovery problems in this chapter, and generalize the results we obtained in 
Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.  
Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  Questions on
optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.

Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in Section \ref{subsec:sufficient}.  A very general class of 
dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us 
for the necessary condition in Section \ref{subsec:necessary}.
Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.

@@

%\section{Exact support recovery under AGG errors}
%\label{sec:boundary}
\input{4.exact_support_recovery/4.phase_transition_results.tex}

@@
